The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-15 paper/ms.tex
minor changes
revised abstract

\begin{abstract}
%For the first the effect of gas bulk rotation on the morphology 
%of the Lyman $\alpha$ line is studied using radiative transfer calculations.
We present results of radiative transfer calculations to measure
the impact of gas bulk rotation on the morphology of the Lyman $\alpha$ line in galaxies. 
We model a galaxy as a sphere with a
homogeneous mixture of dust and hydrogen at a constant
temperature. These spheres have a solid-body rotation with
maximum velocities in the range $0-300$ \kms and neutral
hydrogen optical depths in the range $\tau_{\rm
H}=10^{5}-10^{7}$. We also consider two kinds of spatial
distribution for the radiation sources with respect to the sphere:
central and homogeneous. We find that the line width and the intensity
at the line's center increases with rotational velocity. In the case of homogeneously distributed
sources, for large rotational velocities the line transforms from a
double peak to a single peak at the line center. Under the same
conditions the escape fraction increases $\sim 30\%$. For
radiation sources located off-center, the line morphology presents a
range of single, double and triple peaked lines. We show how these results are
useful to interpret recent spectroscopic results of distant $z\sim 2-3$ star
forming galaxies.
\end{abstract}

\begin{keywords}
{galaxies: high-redshift,galaxies: star formation, line: formation}
\end{keywords}

>>>>

\begin{abstract}

We present results of radiative transfer calculations to measure the
impact of gas bulk rotation on the morphology of the Lyman $\alpha$
emission line in distant galaxies. We model a galaxy as a sphere with
a homogeneous mixture of dust and hydrogen at a constant
temperature. These spheres have a solid-body rotation with maximum
velocities in the range $0-300$ \kms and neutral hydrogen optical
depths in the range $\tau_{\rm H}=10^{5}-10^{7}$. We also consider two
kinds of spatial distribution for the radiation sources with respect
to the sphere: central and homogeneous. Our main finding is that the
line width and the intensity at the line's center increase with
rotational velocity. For homogeneously distributed sources the line
becomes single peaked at large rotational velocities. Under the same
conditions the escape fraction increases $\sim 30\%$. For radiation
sources located off-center, the line morphology presents a range of
single, double and triple peaks. We show how these results are useful
to interpret recent spectroscopic results of distant $z\sim 2-3$ star
forming galaxies. 
\end{abstract}

\begin{keywords}
{galaxies: high-redshift, galaxies: star formation, line: formation}
\end{keywords}
